---
title: "1. Merging"
author: "Helena Davies"
date: "20/08/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Mood Disorder Questionnaire (MDQ): Mania symptoms - for GLAD, EDGI, and NBR
Read in data 
```{r Read in data mdq}
# EDGI
mdq_edgi_signup <- readRDS(file = paste0(filepath, "/latest_freeze/edgi/clinical/mdq_edgi_clean.rds"))

mdq_edgi_signup %>%
  dim()

mdq_edgi_signup %>%
  colnames()

# Select columns
mdq_edgi_signup <- mdq_edgi_signup %>%
  select(ID,
         sample, 
         mdq.hyper_normal_people_thought.1_numeric,                         
         mdq.start_fights_shouted_arguments.1_numeric,                      
         mdq.usual_felt_selfconfident.1_numeric,                             
         mdq.miss_found_sleep_usual.1_numeric,                               
         mdq.faster_spoke_talkative_usual.1_numeric,                         
         mdq.head_mind_couldnt_slow.1_numeric,                               
         mdq.staying_track_trouble_concentrating.1_numeric,                  
         mdq.you_had_much_more_energy_than_usual.1_numeric,                  
         mdq.active_usual_things.1_numeric,                              
         mdq.outgoing_middle_night_usual.1_numeric,                      
         mdq.interested_sex_usual.1_numeric,                                 
         mdq.excessive_foolish_risky_unusual.1_numeric,                  
         mdq.trouble_family_spending_money.1_numeric
         )

# EDGI COPING
mdq_edgi_cop <- readRDS(file = paste0(filepath, "/latest_freeze/coping_edgi/clinical/mdq_coping_edgi_clean.rds"))

mdq_edgi_cop %>%
  dim()

mdq_edgi_cop %>%
  colnames()

# Select columns
mdq_edgi_cop <- mdq_edgi_cop %>%
  select(ID,
         sample,
         mdq.hyper_normal_people_thought.1_cop_numeric,                         
         mdq.start_fights_shouted_arguments.1_cop_numeric,                      
         mdq.usual_felt_selfconfident.1_cop_numeric,                             
         mdq.miss_found_sleep_usual.1_cop_numeric,                               
         mdq.faster_spoke_talkative_usual.1_cop_numeric,                         
         mdq.head_mind_couldnt_slow.1_cop_numeric,                               
         mdq.staying_track_trouble_concentrating.1_cop_numeric,                  
         mdq.you_had_much_more_energy_than_usual.1_cop_numeric,                  
         mdq.active_usual_things.1_cop_numeric,                              
         mdq.outgoing_middle_night_usual.1_cop_numeric,                      
         mdq.interested_sex_usual.1_cop_numeric,                                 
         mdq.excessive_foolish_risky_unusual.1_cop_numeric,                  
         mdq.trouble_family_spending_money.1_cop_numeric
  )


# Merge EDGI and EDGI COPING
# the MDQ was optional in EDGI but compulsory in COPING. So, there might be some people who are in one dataset but not another.
mdq_edgi <- dplyr::full_join(mdq_edgi_cop,
                          mdq_edgi_signup,
                          by = c("ID",
                                  "sample"
                                  )
)


# Check
mdq_edgi %>%
  dim()

# GLAD 
mdq_glad <- readRDS(file = paste0(filepath, "/latest_freeze/glad/clinical/mdq_glad_clean.rds"))

mdq_glad %>%
  dim()

mdq_glad %>%
  colnames()

# Select columns
mdq_glad <- mdq_glad %>%
  select(ID,
         sample,
         mdq.hyper_normal_people_thought.1_numeric,
         mdq.start_fights_shouted_arguments.1_numeric,
         mdq.usual_felt_selfconfident.1_numeric,
         mdq.miss_found_sleep_usual.1_numeric,
         mdq.faster_spoke_talkative_usual.1_numeric,
         mdq.head_mind_couldnt_slow.1_numeric,
         mdq.staying_track_trouble_concentrating.1_numeric,
         mdq.you_had_much_more_energy_than_usual.1_numeric,
         mdq.active_usual_things.1_numeric,
         mdq.outgoing_middle_night_usual.1_numeric,
         mdq.interested_sex_usual.1_numeric,
         mdq.excessive_foolish_risky_unusual.1_numeric,
         mdq.trouble_family_spending_money.1_numeric
  )


# NBR
mdq_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_nbr/clinical/mdq_coping_nbr_clean.rds"))

mdq_nbr %>%
  dim()

mdq_nbr %>%
  colnames()

# Select columns
mdq_nbr <- mdq_nbr %>%
  select(ID,
         sample,
         mdq.hyper_normal_people_thought.1_cop_numeric,                         
         mdq.start_fights_shouted_arguments.1_cop_numeric,                      
         mdq.usual_felt_selfconfident.1_cop_numeric,                             
         mdq.miss_found_sleep_usual.1_cop_numeric,                               
         mdq.faster_spoke_talkative_usual.1_cop_numeric,                         
         mdq.head_mind_couldnt_slow.1_cop_numeric,                               
         mdq.staying_track_trouble_concentrating.1_cop_numeric,                  
         mdq.you_had_much_more_energy_than_usual.1_cop_numeric,                  
         mdq.active_usual_things.1_cop_numeric,                              
         mdq.outgoing_middle_night_usual.1_cop_numeric,                      
         mdq.interested_sex_usual.1_cop_numeric,                                 
         mdq.excessive_foolish_risky_unusual.1_cop_numeric,                  
         mdq.trouble_family_spending_money.1_cop_numeric
  )

# Bind mdq data
mdq <- mdq_edgi %>%
  bind_rows(mdq_glad,
            mdq_nbr)

# Check 
mdq %>%
  nrow()

mdq %>%
  colnames()    
```

# Ethnicity
Merged: GLAD, EDGI, NBR COPING 
Read in data
```{r read in ethnicity data}
# GLAD & EDGI
ethnicity_glad_edgi <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/ethnicity_glad_edgi_clean.rds"))

ethnicity_glad_edgi %>%
  dim()

ethnicity_glad_edgi %>%
  colnames()

ethnicity_glad_edgi <- ethnicity_glad_edgi %>%
  select(ID,
         sample,
         ethnicity = dem.what_is_your_ethnic_origin
         )

# NBR
ethnicity_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_nbr/demographics/ethnicity_coping_nbr_clean.rds"))

ethnicity_nbr %>%
  dim()

ethnicity_nbr %>%
  colnames()

ethnicity_nbr <- ethnicity_nbr %>%
  select(ID,
         sample,
         ethnicity = dem.what_is_your_ethnic_origin_cop
         )

# Bind
ethnicity <- ethnicity_nbr %>%
  bind_rows(ethnicity_glad_edgi)
```

# ED100K: Eating disorder diagnoses from DSM-5 algorithm
Merged: GLAD optional, GLAD COPING, EDGI, NBR COPING
Read in data
```{r Read in data ed.diagnoses}
# GLAD
ed_diagnoses_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad/algorithms/ed_algorithms_diagnostics_glad_clean.rds"))

ed_diagnoses_glad_signup %>%
  dim()

ed_diagnoses_glad_signup %>%
  colnames()

# Select columns
ed_diagnoses_glad_signup <- ed_diagnoses_glad_signup %>%
  select(ID,
         sample,
         ed.DSM5_AN_binary_numeric,
         ed.DSM5_AN_binary,
         ed.DSM5_AN_restricting_binary,
         ed.DSM5_AN_restricting_binary_numeric,
         ed.DSM5_AN_binge_purge_binary_numeric,
         ed.DSM5_AN_binge_purge_binary,
         ed.DSM5_AN_binge_only_binary_numeric,
       #  ed.DSM5_AN_binge_only_binary,
         ed.DSM5_AN_purge_only_binary_numeric,
       #  ed.DSM5_AN_purge_only_binary,
         ed.DSM5_BED_binary,
         ed.DSM5_BED_binary_numeric,
         ed.DSM5_BN_binary,
         ed.DSM5_BN_binary_numeric
         )

# GLAD COPING
ed_diagnoses_glad_cop <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad/algorithms/ed_algorithms_diagnostics_coping_glad_clean.rds"))

ed_diagnoses_glad_cop %>%
  dim()

ed_diagnoses_glad_cop %>%
  colnames()

# Select columns
ed_diagnoses_glad_cop <- ed_diagnoses_glad_cop %>%
  select(ID,
         sample,
         ed.DSM5_AN_binary_numeric_cop,
         ed.DSM5_AN_binary_cop,
         ed.DSM5_AN_restricting_binary_cop,
         ed.DSM5_AN_restricting_binary_numeric_cop,
         ed.DSM5_AN_binge_purge_binary_numeric_cop,
         ed.DSM5_AN_binge_purge_binary_cop,
         ed.DSM5_BED_binary_cop,
         ed.DSM5_BED_binary_numeric_cop,
         ed.DSM5_BN_binary_cop,
         ed.DSM5_BN_binary_numeric_cop,
         ed.DSM5_AN_binge_only_binary_numeric_cop,
         ed.DSM5_AN_binge_only_binary_cop,
         ed.DSM5_AN_purge_only_binary_numeric_cop,
         ed.DSM5_AN_purge_only_binary_cop
         )


# Merge GLAD and GLAD COPING
# the ED100K was optional in GLAD but compulsory in COPING. So, there might be some people who are in one dataset but not another.
ed_diagnoses_glad <- dplyr::full_join(ed_diagnoses_glad_cop,
                          ed_diagnoses_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
ed_diagnoses_glad %>%
  dim()

# Check
ed_diagnoses_glad %>%
  nrow()

ed_diagnoses_glad %>%
  colnames()

# EDGI
ed_diagnoses_edgi <- readRDS(file = paste0(filepath, "/latest_freeze/edgi/algorithms/ed_algorithms_diagnostics_edgi_clean.rds"))

ed_diagnoses_edgi %>%
  dim()

ed_diagnoses_edgi %>%
  colnames()

# NBR
ed_diagnoses_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_nbr/algorithms/ed_algorithms_diagnostics_coping_nbr_clean.rds"))

ed_diagnoses_nbr %>%
  dim()

ed_diagnoses_nbr %>%
  colnames()

# Select columns
ed_diagnoses_nbr <- ed_diagnoses_nbr %>%
  select(ID,
         sample,
         ed.DSM5_AN_binary_numeric_cop,
         ed.DSM5_AN_binary_cop,
         ed.DSM5_AN_restricting_binary_cop,
         ed.DSM5_AN_restricting_binary_numeric_cop,
         ed.DSM5_AN_binge_purge_binary_numeric_cop,
         ed.DSM5_AN_binge_purge_binary_cop,
         ed.DSM5_BED_binary_cop,
         ed.DSM5_BED_binary_numeric_cop,
         ed.DSM5_BN_binary_cop,
         ed.DSM5_BN_binary_numeric_cop
         )

# Merge all data
ed_diagnoses <- ed_diagnoses_glad %>%
  bind_rows(ed_diagnoses_edgi,
            ed_diagnoses_nbr
            )

# Check
ed_diagnoses %>%
  dim()

ed_diagnoses %>%
  colnames()
```

# ED100K: Self-report eating disorder diagnoses 
Merged: GLAD optional
Read in data
```{r Read in data ed.diagnoses}
ed_selfreport_diagnoses_GLAD <- readRDS(file = paste0(filepath, "/latest_freeze/glad/eating/selfreported_ed100k_diagnoses_glad_clean.rds"))

ed_selfreport_diagnoses_GLAD %>%
  dim()

ed_selfreport_diagnoses_GLAD %>%
  colnames()
```

# Mental health diagnosis questionnaire (MHD): Self-reported eating disorder diagnoses
Merged: GLAD, GLAD COPING, EDGI, EDGI COPING, NBR COPING
Read in data
```{r Read in data}
# GLAD, EDGI
mhd_glad_edgi <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/clinical/mhd_glad_edgi_clean.rds"))

mhd_glad_edgi %>%
  dim()

mhd_glad_edgi %>%
  colnames()

excluded_vars <- c("startDate",
                   "endDate"
                   )

mhd_glad_edgi <- mhd_glad_edgi %>%
  select(-one_of(excluded_vars))

# GLAD COPING & NBR 
mhd_coping_glad_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_nbr/clinical/mhd_coping_glad_nbr_clean.rds"))

mhd_coping_glad_nbr %>%
  dim()

mhd_coping_glad_nbr %>%
  colnames()

mhd_coping_glad_nbr <- mhd_coping_glad_nbr %>%
  select(-one_of(excluded_vars))

# Merge
mhd <- dplyr::full_join(mhd_glad_edgi,
                          mhd_coping_glad_nbr,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
mhd %>%
  dim()

mhd %>%
  nrow()
```

# ED100K disordered eating symptoms
Merged: GLAD, GLAD COPING, EDGI, EDGI COPING, NBR COPING
Read in data
```{r Read in data binge_eating}
# GLAD & EDGI
disordered_eating_symptoms_glad_edgi_signup  <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/behaviours/ED_behaviours_glad_edgi_clean.rds"))

disordered_eating_symptoms_glad_edgi_signup  %>%
  dim()

disordered_eating_symptoms_glad_edgi_signup %>%
  colnames()

disordered_eating_symptoms_glad_edgi_signup <- disordered_eating_symptoms_glad_edgi_signup %>%
  select(ID,
         sample,
         binge_eating = be.short_period_ate_regard,
         loss_of_control = be.binge_eating_stop_eating
         )

# GLAD COPING 
disordered_eating_symptoms_glad_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad/behaviours/ED_behaviours_coping_glad_clean.rds"))

disordered_eating_symptoms_glad_coping %>%
  dim()

disordered_eating_symptoms_glad_coping %>%
  colnames()

disordered_eating_symptoms_glad_coping <- disordered_eating_symptoms_glad_coping %>%
  select(ID,
         sample,
         binge_eating_cop = be.short_period_ate_regard_cop,
         loss_of_control_cop = be.binge_eating_stop_eating_cop
         )

# Merge GLAD & EDGI with GLAD COPING
disordered_eating_symptoms_glad_edgi <- dplyr::full_join(disordered_eating_symptoms_glad_coping,
                          disordered_eating_symptoms_glad_edgi_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
disordered_eating_symptoms_glad_edgi %>%
  dim()

# Check
disordered_eating_symptoms_glad_edgi %>%
  nrow()

# NBR
disordered_eating_symptoms_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_nbr/behaviours/ED_behaviours_nbr_clean.rds"))

disordered_eating_symptoms_nbr %>%
  dim()

disordered_eating_symptoms_nbr %>%
  colnames()

disordered_eating_symptoms_nbr <- disordered_eating_symptoms_nbr %>%
  select(ID,
         sample,
         binge_eating_cop = be.short_period_ate_regard_coping,
         loss_of_control_cop = be.binge_eating_stop_eating_coping
         )

# Bind
disordered_eating_symptoms <- disordered_eating_symptoms_glad_edgi %>%
  bind_rows(disordered_eating_symptoms_nbr)
```

# Age 
Merged: GLAD, EDGI COPING, NBR COPING (NB: want to adjust symptoms for age)
Read in data
```{r Read in data age}
# GLAD & EDGI
age_glad_edgi_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/age_glad_edgi_clean.rds"))

age_glad_edgi_signup %>%
  dim()

age_glad_edgi_signup %>%
  colnames()

age_glad_edgi_signup <- age_glad_edgi_signup %>%
  select(ID,
         sample,
         selfreported_age = dem.how_old_are_you_now.txt,
         dem.dob_age,
         dem.age_category
         )

# GLAD COPING, EDGI COPING, & NBR
age_coping_glad_edgi_nbr <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/age_coping_glad_edgi_nbr_clean.rds"))

age_coping_glad_edgi_nbr %>%
  dim()

age_coping_glad_edgi_nbr %>%
  colnames()


age_coping_glad_edgi_nbr <- age_coping_glad_edgi_nbr %>%
  select(ID,
         sample,
         dem.dob_age_cop,
         dem.age_category_cop
         )

# Merge
age <- dplyr::full_join(age_glad_edgi_signup,
                          age_coping_glad_edgi_nbr,
                          by = c("ID",
                                  "sample"
                                  )
)
```

# Sex 
Merged: GLAD, EDGI COPING, NBR COPING (NB: want to adjust symptoms for sex)
Read in data
```{r Read in data sex}
# GLAD & EDGI
sex_gender_edgi_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/sex_gender_sexuality_glad_edgi_clean.rds"))

sex_gender_edgi_glad_signup %>%
  colnames()

sex_gender_edgi_glad_signup %>%
  dim()

sex_gender_edgi_glad_signup <- sex_gender_edgi_glad_signup %>%
  select(ID,
         sample,
         sex_numeric = dem.sex_numeric,
         sex = dem.sex,
         gender = dem.which_gender_do_you_identify_with,
         gender_numeric = dem.which_gender_do_you_identify_with_numeric,
         transgender = dem.do_you_identify_as_transgender,
         transgender_numeric = dem.do_you_identify_as_transgender_numeric
         )

# GLAD COPING, EDGI COPING, & NBR
sex_gender_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/sex_gender_sexuality_coping_glad_edgi_nbr_clean.rds"))

sex_gender_coping %>%
  colnames()

sex_gender_coping %>%
  dim()

sex_gender_coping <- sex_gender_coping %>%
  select(ID,
         sample,
         sex_cop = dem.sex_cop,
         sex_cop_numeric =  dem.sex_cop_numeric,
         gender_cop = dem.which_gender_do_you_identify_with_cop,
          gender_cop_numeric = dem.which_gender_do_you_identify_with_cop_numeric,
          transgender_cop = dem.do_you_identify_as_transgender_cop,
          transgender_cop_numeric = dem.do_you_identify_as_transgender_cop_numeric
         )

# Merge data
sex_gender <- dplyr::full_join(sex_gender_coping,
                          sex_gender_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
sex_gender %>%
  dim()

# Check
sex_gender %>%
  nrow()
```
 
# Highest education 
Merged: GLAD, EDGI COPING, NBR COPING 
Read in data
```{r Read in data education.years }
# GLAD & EDGI
highest_education_edgi_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/highest_education_glad_edgi_clean.rds"))

highest_education_edgi_glad_signup %>%
  colnames()

highest_education_edgi_glad_signup %>%
  dim()

highest_education_edgi_glad_signup <- highest_education_edgi_glad_signup %>%
  select(ID,
        sample,
        dem.highest_education_collapsed,
        dem.highest_education_finegrained
        )

# GLAD COPING, EDGI COPING, & NBR
highest_education_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/highest_education_coping_glad_edgi_nbr_clean.rds"))

highest_education_coping %>%
  colnames()

highest_education_coping %>%
  dim()

highest_education_coping <- highest_education_coping %>%
  select(ID,
        sample,
        employ.highest_education_collapsed_cop,
        employ.highest_education_finegrained_cop
        )

# Merge GLAD COPING, EDGI COPING, & NBR with GLAD & EDGI
highest_education <- dplyr::full_join(highest_education_coping,
                          highest_education_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
highest_education %>%
  colnames()

# Check
highest_education %>%
  nrow()
```

# BMI (at time of assessment) 
Merged: GLAD sign-up, EDGI sign-up, NBR COPING 
Read in data
```{r Read in data bmi}
# GLAD & EDGI
bmi_edgi_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/signup_bmi_height_weight_glad_edgi_clean.rds"))

bmi_edgi_glad_signup %>%
  colnames()

bmi_edgi_glad_signup %>%
  dim()

bmi_edgi_glad_signup <- bmi_edgi_glad_signup %>%
  select(ID,
         sample, 
         dem.bmi_signup
         )

# GLAD COPING, EDGI COPING, & NBR
bmi_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/signup_bmi_height_weight_coping_glad_edgi_nbr_clean.rds"))

bmi_coping %>%
  colnames()

bmi_coping %>%
  dim()

bmi_coping <- bmi_coping %>%
  select(ID,
         sample, 
         dem.bmi_signup_cop
         )

# Merge GLAD COPING, EDGI COPING, & NBR with GLAD & EDGI
bmi_at_assessment <- dplyr::full_join(bmi_coping,
                          bmi_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
bmi_at_assessment %>%
  dim()

# Check
bmi_at_assessment %>%
  nrow()
```

# Lowest BMI 
Merged: GLAD, GLAD COPING, EDGI, EDGI COPING, NBR (AN lowest BMI not assessed in EDGI COPING)
Read in data
```{r Read in data bmi}
# GLAD & EDGI
lowest_bmi_edgi_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/lowest_bmi_height_weight_glad_edgi_clean.rds"))

lowest_bmi_edgi_glad_signup %>%
  colnames()

lowest_bmi_edgi_glad_signup %>%
  dim()

lowest_bmi_edgi_glad_signup <- lowest_bmi_edgi_glad_signup %>%
  select(ID,
         sample, 
         dem.bmi_lowest,
         an.bmi_lowest
         )

# GLAD COPING, EDGI COPING, & NBR
lowest_bmi_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/lowest_bmi_height_weight_coping_glad_edgi_nbr_clean.rds"))

lowest_bmi_coping %>%
  colnames()

lowest_bmi_coping %>%
  dim()

lowest_bmi_coping <- lowest_bmi_coping %>%
  select(ID,
         sample, 
         dem.bmi_lowest_cop,
         an.bmi_lowest_cop
         )

# Merge GLAD COPING, EDGI COPING, & NBR with GLAD & EDGI
bmi_lowest <- dplyr::full_join(lowest_bmi_coping,
                          lowest_bmi_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
bmi_lowest %>%
  dim()

# Check
bmi_lowest %>%
  nrow()
```

# Highest BMI
Merged: GLAD, GLAD COPING, EDGI, EDGI COPING, NBR
Read in data
```{r Read in data bmi}
# GLAD & EDGI
highest_bmi_edgi_glad_signup <- readRDS(file = paste0(filepath, "/latest_freeze/glad_edgi/demographics/highest_bmi_height_weight_glad_edgi_clean.rds"))

highest_bmi_edgi_glad_signup %>%
  colnames()

highest_bmi_edgi_glad_signup %>%
  dim()

highest_bmi_edgi_glad_signup <- highest_bmi_edgi_glad_signup %>%
  select(ID,
         sample, 
         dem.bmi_highest
         )

# GLAD COPING, EDGI COPING, & NBR
highest_bmi_coping <- readRDS(file = paste0(filepath, "/latest_freeze/coping_glad_edgi_nbr/demographics/highest_bmi_weight_coping_glad_edgi_nbr_clean.rds"))

highest_bmi_coping %>%
  colnames()

highest_bmi_coping %>%
  dim()

highest_bmi_coping <- highest_bmi_coping %>%
  select(ID,
         sample, 
         dem.bmi_highest_cop
         )

# Merge GLAD COPING, EDGI COPING, & NBR with GLAD & EDGI
bmi_highest <- dplyr::full_join(highest_bmi_coping,
                          highest_bmi_edgi_glad_signup,
                          by = c("ID",
                                  "sample"
                                  )
)

# Check
bmi_highest %>%
  dim()

# Check
bmi_highest %>%
  nrow()
```

# Merge data
```{r merge data}
# Merge all data
dat_1 <- dplyr::full_join(mdq,
                          ethnicity,
                          by = c("ID",
                "sample"
                )
         )

dat_2 <- dplyr::full_join(dat_1,
                          ed_diagnoses,
                          by = c("ID",
                "sample"
                )
         )
  
dat_3 <- dplyr::full_join(dat_2,
                          ed_selfreport_diagnoses_GLAD,
                          by = c("ID",
                "sample"
                )
         )
  
dat_4 <- dplyr::full_join(dat_3,
                          disordered_eating_symptoms,
                          by = c("ID",
                "sample"
                )
         )

dat_5 <- dplyr::full_join(dat_4,
                          age,
                          by = c("ID",
                "sample"
                )
         )

dat_6 <- dplyr::full_join(dat_5,
                          sex_gender,
                          by = c("ID",
                "sample"
                )
         )

dat_7 <- dplyr::full_join(dat_6,
                          highest_education,
                          by = c("ID",
                "sample"
                )
         )

dat_8 <- dplyr::full_join(dat_7,
                          mhd,
                          by = c("ID",
                "sample"
                )
         )

dat_9 <- dplyr::full_join(dat_8,
                          bmi_at_assessment,
                          by = c("ID",
                "sample"
                )
         )


dat_10 <- dplyr::full_join(dat_9,
                          bmi_lowest,
                          by = c("ID",
                "sample"
                )
         )

dat_merged <- dplyr::full_join(dat_10,
                          bmi_highest,
                          by = c("ID",
                "sample"
                )
         )

# Check
dat_merged %>%
  colnames()

dat_merged %>%
  dim()
```

# Recode -777 to NA_real_
```{r}
dat_merged_NA_rm <- dat_merged %>%
  mutate_if(is.numeric, ~na_if(., -888)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -999)) %>%
  mutate_if(is.numeric, ~na_if(., -777)) %>%
  mutate_if(is.numeric, ~na_if(., -666)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
```

# Save merged data
```{r save merged data}
dat_merged_NA_rm %>% 
  saveRDS(
    file = paste0("../data/dat_merged_", 
    date, 
    ".rds"
    )
    )
```