---
title: "1a.GLAD_EDGI_duplicates"
author: "Helena Davies"
date: "30/11/2021"
output: html_document
---

NB: These are duplicated IDs from *registration*. Therefore, there will be some people who have missing data for all questionnaires within a sign-up survey (i.e., they never actually did the survey).
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "skimr", "psych", "rstatix", "gt", "broom", "scales",
              "tidyverse" )
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in duplicated people sheet
```{r read in duplicated people sheet}
dup_people <- read_csv(file = paste0(filepath_Net_raw, "/duplicate_participant_report_2021_11_30_hashed.csv"))
# 882 people
```

Filter out people in main dataset with same ID
```{r}
dat <- readRDS(file = paste0("../../data/dat_merged_2023-04-05.rds"))
dim(dat)
colnames(dat)

# Filter full data for GLAD data (also EDGI participants, 556)
same_people_GLAD_dat <- dat %>%
  filter(ID %in% dup_people$hash_id_GLAD)

# Filter full data for EDGI data (also GLAD participants, 551)
same_people_EDGI_dat <- dat %>%
  filter(ID %in% dup_people$hash_id_EDGI)
```

*We want to keep*:
1) People who filled out the ED100K in EDGI 
2) If not in EDGI (perhaps they never finished the survey), then people who filled out the ED100K in GLAD or GLAD COPING 

Who has filled out the EDGI ED100K?
```{r look at ED frequency}
# Filled out EDGI ED100K
EDGI_dat_ED100k <- same_people_EDGI_dat %>%
  filter( 
    # ED100K 
         !is.na(ed.DSM5_AN_binary_numeric) |
         !is.na(ed.DSM5_AN_restricting_binary_numeric) |
         !is.na(ed.DSM5_AN_binge_purge_binary_numeric)  |
         !is.na(ed.DSM5_BN_binary_numeric)  |  
         !is.na(ed.DSM5_BED_binary_numeric) |
         !is.na(binge_eating)
           ) %>%
  pull(ID) 

# For these people, we want their GLAD ID (to check if they have done the GLAD ED100K)
no_EDGI_dat_ED100k_GLAD_IDs <- dup_people %>%
 filter(hash_id_EDGI %!in% EDGI_dat_ED100k) %>%
  pull(hash_id_GLAD)

# People  who have not filled out the EDGI ED100K - have they filled it out in GLAD COPING? (The ED100K was not asked again in EDGI...this would be a more recent entry than their GLAD entry so should take these if poss)
GLAD_ED100K_check_cop <- same_people_GLAD_dat %>%
  filter(ID %in% no_EDGI_dat_ED100k_GLAD_IDs &
    # GLAD 
         (!is.na(ed.DSM5_AN_binary_numeric_cop) |
         !is.na(ed.DSM5_AN_restricting_binary_numeric_cop) |
         !is.na(ed.DSM5_AN_binge_purge_binary_numeric_cop)  |
         !is.na(ed.DSM5_BN_binary_numeric_cop)  |  
         !is.na(ed.DSM5_BED_binary_numeric_cop) |
         !is.na(binge_eating_cop))
           ) %>%
  pull(ID) 

# People people who have not filled out the EDGI ED100K - have they filled it out in GLAD?
GLAD_ED100K_check <- same_people_GLAD_dat %>%
  filter(
    # Have not filled out the EDGI ED100K or the GLAD COPING ED100K
    (ID %in% no_EDGI_dat_ED100k_GLAD_IDs &
         ID %!in% GLAD_ED100K_check_cop) &
   
         (!is.na(ed.DSM5_AN_binary_numeric) |
         !is.na(ed.DSM5_AN_restricting_binary_numeric) |
         !is.na(ed.DSM5_AN_binge_purge_binary_numeric)  |
         !is.na(ed.DSM5_BN_binary_numeric)  |  
         !is.na(ed.DSM5_BED_binary_numeric) |
         !is.na(binge_eating))
           ) %>%
  pull(ID) 

# Merge GLAD IDs to keep (i.e., people who did not fill out the EDGI ED100K but did so in GLAD COPING or GLAD signup)
GLAD_IDs_to_keep <- c(GLAD_ED100K_check_cop,
                      GLAD_ED100K_check)  


# For everyone else, we want to keep their EDGI ID (even though there are still ~ 200 people who have not done the EDGI ED100K, they have not filled it out in GLAD or GLAD COPING either, so we will keep their EDGI data as a default as it is likely the most recent and relevant to my projects)
# For these people, we want their GLAD ID (to check if they have done the GLAD ED100K)
EDGI_IDs_to_keep <- dup_people %>%
 filter(hash_id_GLAD %!in% GLAD_IDs_to_keep) %>%
  pull(hash_id_EDGI)

# Merge GLAD and EDGI IDs to keep 
GLAD_EDGI_IDs_to_keep <- c(GLAD_IDs_to_keep,
                      EDGI_IDs_to_keep)  

# Create as dataframe
GLAD_EDGI_IDs_to_keep_dat <- as.data.frame(GLAD_EDGI_IDs_to_keep)
```

Create IDs to drop data frame
```{r create IDs to drop data frame}
EDGI_IDs_to_drop <- dup_people %>%
 filter(hash_id_EDGI %!in% GLAD_EDGI_IDs_to_keep) %>%
  pull(hash_id_EDGI)

GLAD_IDs_to_drop <- dup_people %>%
 filter(hash_id_GLAD %!in% GLAD_EDGI_IDs_to_keep) %>%
  pull(hash_id_GLAD)

# Merge GLAD and EDGI IDs to drop
GLAD_EDGI_IDs_to_drop <- c(GLAD_IDs_to_drop,
                      EDGI_IDs_to_drop)  

GLAD_EDGI_IDs_to_drop_dat <- as.data.frame(GLAD_EDGI_IDs_to_drop)
```

Double check no IDs overlap
```{r checking no overlapping IDs}
overlapping_IDs <- GLAD_EDGI_IDs_to_keep_dat %>%
  filter(GLAD_EDGI_IDs_to_keep %in% GLAD_EDGI_IDs_to_drop_dat$GLAD_EDGI_IDs_to_drop)

overlapping_IDs_2 <- GLAD_EDGI_IDs_to_drop_dat %>%
  filter(GLAD_EDGI_IDs_to_drop %in% GLAD_EDGI_IDs_to_keep_dat$GLAD_EDGI_IDs_to_keep)
```
30/11/21: No IDs overlap!

Export as data frame 
```{r save as data frames}
GLAD_EDGI_IDs_to_drop_dat %>% 
  saveRDS(
    file = paste0("../../data/GLAD_EDGI_IDs_to_drop_dat_", 
    date, 
    ".rds"
    )
    )

GLAD_EDGI_IDs_to_keep_dat %>% 
  saveRDS(
    file = paste0("../../data/GLAD_EDGI_IDs_to_keep_dat_", 
    date, 
    ".rds"
    )
    )
```

