---
title: "3. Exclusions"
author: "Helena Davies"
date: "20/08/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in merged data with variables
```{r read in merged data}
dat <- readRDS(file = paste0("../../data/dat_variables_2022-03-15.rds"))

dat <- dat %>%
  filter(sample != "RAMP")
```

# Check number of overall participants before exclusion
```{r number of participants before exclusion}
dat %>%
  nrow() 
```

# Check where participants are from before exclusion criteria applied - detailed
```{r check NBR cohort information}
cohort_info_detailed <- read_csv(paste0(filepath_PhD, "/COPING_cohorts_28.03.2022_hash.csv"))

cohort_info_detailed <- cohort_info_detailed %>%
  select(ID = hash_id,
         cohort_detailed = panel
         )

cohort_info_detailed %>%
  freq(cohort_detailed)

dat <- dplyr::full_join(dat,
                        cohort_info_detailed,
                        by ="ID")


dat %>%
  filter(sample =="NBR") %>%
  freq(cohort_detailed)

# Check if they have info
dat %>%
  filter(sample =="NBR" &
           is.na(cohort_detailed)) %>%
  freq(gender_cop)


dat %>%
  filter(sample =="NBR" &
        is.na(cohort_detailed) &
          
         (!is.na(dem.dob_age_cop) |
         !is.na(sex_cop) |
           !is.na(mhd.mdd_numeric)) 
         ) %>%
  pull(ID) %>%
  write.table(paste0(filepath_misc, "NBR_IDs_no_cohort_info_NEW_11072022.csv"),
              row.names = F )
```

```{r cohort info less detail}
cohort_info <- read_csv(paste0(filepath_nbr_additional_info, "DEPRECATED_coping_participants_export_20200730_hashed.csv"))

cohort_info <- cohort_info %>%
  select(ID = "NBR ID",
         cohort 
         )

cohort_info %>%
  freq(cohort)

dat <- dplyr::full_join(dat,
                        cohort_info,
                        by ="ID")


dat %>%
  filter(sample =="NBR") %>%
  freq(cohort)
```

  
# Create two datasets
1) Symptom dataset
```{r creating two separate datasets}
# Symptom data
## First, exclude NBR participants with missing cohort information or age or sex (i.e., did not answer questionnaires)
dat <- dat %>%
  filter(
          (sample == "GLAD" |
           sample == "EDGI") |
           
           (
             (sample == "NBR" &
              !is.na(cohort)) |
           
           ((sample == "NBR" &
              is.na(cohort)) &
              !is.na(age_sx_level))
         )
  )
# Check 
dat %>%
  dim()

symptom_dat <- dat %>%
  filter(!is.na(binge_eating_with_loss_control))

# Check 
symptom_dat %>%
  dim()

# Missing for BE
70648-40228
```

#  Symptom data
## Sex
Exclude participants with missing sex
```{r sex missing symptom data}
dim(symptom_dat)
symptom_dat_excl_sex <- symptom_dat %>%
  drop_na(sex_final)
nrow(symptom_dat_excl_sex)-nrow(symptom_dat)
```
678 participants did not report their biological sex

## Age
Exclude participants with missing age
```{r missing age in sample symptom data}
dim(symptom_dat_excl_sex)
symptom_dat_excl_sex_age <- symptom_dat_excl_sex %>%
  drop_na(age_sx_level)
nrow(symptom_dat_excl_sex_age)-nrow(symptom_dat_excl_sex)

nrow(symptom_dat)-nrow(symptom_dat_excl_sex_age) # total


# sensitivity (BE no loss of control)
symptom_dat_excl_sex_age <- symptom_dat_excl_sex_age %>%
  drop_na(age_sx_level_sens)
```
691 participants did not report their age

## MDQ
Exclude participants that had missing MDQ values
```{r mdq exclusion participants with implausible values symptom data}
dim(symptom_dat_excl_sex_age)

symptom_dat_excl_sex_age_mdq <- symptom_dat_excl_sex_age %>%
  drop_na(
      more_hyperactivity_numeric_sx_level,
      more_irritability_numeric_sx_level,
      more_self_confidence_numeric_sx_level,
      less_sleep_numeric_sx_level,      
      more_talkative_numeric_sx_level,
      racing_thoughts_numeric_sx_level,
      conc_difficulties_numeric_sx_level,
      more_energy_numeric_sx_level,
      more_active_numeric_sx_level,
      more_social_numeric_sx_level,  
      higher_libido_numeric_sx_level,
      more_risky_beh_numeric_sx_level,
      reckless_spending_numeric_sx_level,
      
      # Sensitivity analysis (BE no loss of control)
      more_hyperactivity_numeric_sx_level_sens,
      more_irritability_numeric_sx_level_sens,
      more_self_confidence_numeric_sx_level_sens,
      less_sleep_numeric_sx_level_sens,
      more_talkative_numeric_sx_level_sens,
      racing_thoughts_numeric_sx_level_sens,
      conc_difficulties_numeric_sx_level_sens,
      more_energy_numeric_sx_level_sens,
      more_active_numeric_sx_level_sens,
      more_social_numeric_sx_level_sens,
      higher_libido_numeric_sx_level_sens,
      more_risky_beh_numeric_sx_level_sens,
      reckless_spending_numeric_sx_level_sens
    )
nrow(symptom_dat_excl_sex_age_mdq)-nrow(symptom_dat_excl_sex)

nrow(symptom_dat)-nrow(symptom_dat_excl_sex_age_mdq) # total
```
5076 individuals excluded because they are missing an item on the MDQ.

### Tidy tibble for analysis
```{r Tidy tibble for analysis symptom data}
symptom_dat_analysis <- symptom_dat_excl_sex_age_mdq
```

# Check number of participants and sample origin after exclusion criteria applied
```{r check Ns after exclusion criteria applied}
# Overall
symptom_dat_main_analysis <-  symptom_dat_analysis %>%
  filter(binge_eating_with_loss_control == "BE loss control" |
             binge_eating_with_loss_control == "No BE") 

symptom_dat_analysis %>%
  filter(binge_eating_with_loss_control == "BE loss control" |
             binge_eating_with_loss_control == "No BE") %>%
  freq(sample)

# cohorts within the NBR sample
symptom_dat_analysis %>%
  filter(sample =="NBR" &
           (binge_eating_with_loss_control == "BE loss control" |
             binge_eating_with_loss_control == "No BE")) %>%
  freq(cohort)
```

## Read in revised diagnosis data
```{r revised diagnosis data}
revised_diag_dat <- readRDS(file = "../../data/dat_variables_2023-04-11.rds")

# Select those in original symptom dataset
revised_diag_dat <- revised_diag_dat %>%
  filter(ID %in% symptom_dat_analysis$ID)
```

# 2) Diagnosis dataset
```{r create diagnosis dataset}
diagnosis_dat <- revised_diag_dat %>%
  filter(bulimia_nervosa == 1 |
           anorexia_nervosa_binge_purge == 1 |
           binge_eating_disorder == 1)

# Check 
diagnosis_dat %>%
  dim()

diagnosis_dat %>%
  freq(bulimia_nervosa)

diagnosis_dat %>%
  freq(anorexia_nervosa_binge_purge)

diagnosis_dat %>%
  freq(binge_eating_disorder)

4075+825+5563 # 10463 with EDs
```

# Exclusions for missingness 
# Diagnosis data
## Sex
Exclude participants with missing sex
```{r sex missing diagnosis data}
dim(diagnosis_dat)
diagnosis_dat_excl_sex <- diagnosis_dat %>%
  drop_na(sex_final)
nrow(diagnosis_dat_excl_sex)-nrow(diagnosis_dat)
```
538 participants did not report their biological sex

## Age
Exclude participants with missing age
```{r missing age in sample diagnosis data}
dim(diagnosis_dat_excl_sex)
diagnosis_dat_excl_sex_age <- diagnosis_dat_excl_sex %>%
  drop_na(age_dx_level)
nrow(diagnosis_dat_excl_sex_age)-nrow(diagnosis_dat_excl_sex)
```
A further 0 participants did not report their age

## MDQ
Exclude participants that had missing MDQ values
```{r mdq exclusion participants with implausible values diagnosis data}
dim(diagnosis_dat_excl_sex_age)

diagnosis_dat_excl_sex_age_mdq <- diagnosis_dat_excl_sex_age %>%
  drop_na(
      more_hyperactivity_dx_level,
      more_irritability_dx_level,
      more_self_confidence_dx_level,
      less_sleep_dx_level,      
      more_talkative_dx_level,
      racing_thoughts_dx_level,
      conc_difficulties_dx_level,
      more_energy_dx_level,
      more_active_dx_level,
      more_social_dx_level,  
      higher_libido_dx_level,
      more_risky_beh_dx_level,
      reckless_spending_dx_level
    )
nrow(diagnosis_dat_excl_sex_age_mdq)-nrow(diagnosis_dat_excl_sex)
```
An additional 0 individuals excluded because they are missing an item on the mdq

### Tidy tibble for analysis
```{r Tidy tibble for analysis diagnosis data}
diagnosis_dat_analysis <- diagnosis_dat_excl_sex_age_mdq
```

## Save tidy data
```{r Save data in rds files}
# Export diagnosis data
saveRDS(diagnosis_dat_analysis,
  file = paste0("../../data/diagnosis_dat_analysis",
                date,
                ".rds"
                )
)

# Export symptom data
saveRDS(symptom_dat_analysis,
  file = paste0("../../data/symptom_dat_analysis",
                date,
                ".rds"
                )
)

# Export excluded data
dat %>%
  filter(ID %!in% symptom_dat_main_analysis$ID) %>%
  saveRDS(file = paste0("../../data/excluded_dat_analysis",
                date,
                ".rds"
                )
)
```

