---
title: "Comparing excluded to non-excluded participants"
author: "Helena Davies"
date: "04/04/2022"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in data
```{r read in merged data}
symptom_dat <- readRDS(file = paste0("../data/symptom_dat_analysis2022-03-15.rds"))
dim(symptom_dat) 
colnames(symptom_dat)

excluded_dat <- readRDS(file = paste0("../data/excluded_dat_analysis2022-07-08.rds"))
dim(excluded_dat) 
colnames(excluded_dat)

demographic_dat <- readRDS(file = paste0("../data/dat_variables_2022-03-15.rds"))
dim(demographic_dat) 
colnames(demographic_dat)
```

```{r create excluded variable}
excluded_dat <- excluded_dat %>%
  mutate(excluded =
           case_when(
             ID %in% excluded_dat$ID ~ 1
           ))

symptom_dat <- symptom_dat %>%
  mutate(excluded =
           case_when(
             ID %in% symptom_dat$ID ~ 0
           ))
```

```{r select variables}
symptom_dat <- symptom_dat %>%
  filter(binge_eating_with_loss_control == "No BE" |
         binge_eating_with_loss_control == "BE loss control") %>%
  select(ID,
         excluded,
         sex_final,
         age_dem = age_sx_level,
         bmi_signup_dem = bmi_signup_sx_level,
         bmi_lowest_dem = bmi_lowest_sx_level,
         bmi_highest_dem = bmi_highest_sx_level,
         racially_minoritised,
         highest_education = highest_education_sx_level
         )

excluded_dat <- excluded_dat %>%
  select(ID,
         excluded)

demographic_dat <- demographic_dat %>%
  select(ID,
         dem.bmi_signup,
         an.bmi_lowest,
         dem.bmi_signup_cop,
         dem.bmi_lowest,
         an.bmi_lowest_cop,
         dem.bmi_lowest_cop,
         dem.bmi_highest,
         dem.bmi_highest_cop,
         dem.highest_education_collapsed,
         employ.highest_education_collapsed_cop,
         sex_final,
         dem.dob_age,
         dem.dob_age_cop,
         selfreported_age,
         dem.age_category_cop,
         ethnicity,
         racially_minoritised
         )
```

# Merge exlcuded data with demographic data
```{r merge data}
dat <- dplyr::left_join(excluded_dat,
                        demographic_dat,
                        by = "ID")
```

# Create variables based on COPING or GLAD/EDGI data
## Sex
```{r sex check}
dat %>%
  freq(sex_final)
```

## Age
```{r age create variables based on data available}
dat <- dat %>%
  mutate(age_dem =
           case_when(
             !is.na(dem.dob_age) ~ dem.dob_age,
             !is.na(selfreported_age) ~ selfreported_age,
             !is.na(dem.dob_age_cop) ~ dem.dob_age_cop
           ))

# Check
dat %>%
  freq(age_dem)

dat %>%
  filter(is.na(age_dem)) %>%
  freq(dem.dob_age)

dat %>%
  filter(is.na(age_dem)) %>%
  freq(selfreported_age)

dat %>%
  filter(is.na(age_dem)) %>%
  freq(dem.dob_age_cop)

dat %>%
  filter(is.na(age_dem)) %>%
  freq(dem.age_category_cop)
```

## Racially minoritised
```{r racially_minoritised check (already made)}
# Check
dat %>%
  freq(racially_minoritised)
```

## BMI lowest
```{r bmi lowest create variables based on data available}
dat <- dat %>%
  mutate(bmi_lowest_dem =
           case_when(
             !is.na(an.bmi_lowest) ~ an.bmi_lowest,
             !is.na(dem.bmi_lowest) ~ dem.bmi_lowest,
             !is.na(an.bmi_lowest_cop) ~ an.bmi_lowest_cop,
             !is.na(dem.bmi_lowest_cop) ~ dem.bmi_lowest_cop
           ))

# Check
dat %>%
  freq(bmi_lowest_dem)

dat %>%
  filter(is.na(bmi_lowest_dem)) %>%
  freq(an.bmi_lowest)

dat %>%
  filter(is.na(bmi_lowest_dem)) %>%
  freq(dem.bmi_lowest)

dat %>%
  filter(is.na(bmi_lowest_dem)) %>%
  freq(an.bmi_lowest_cop)

dat %>%
  filter(is.na(bmi_lowest_dem)) %>%
  freq(dem.bmi_lowest_cop)
```

## BMI highest
```{r bmi highest create variables based on data available}
dat <- dat %>%
  mutate(bmi_highest_dem =
           case_when(
             !is.na(dem.bmi_highest) ~ dem.bmi_highest,
             !is.na(dem.bmi_highest_cop) ~ dem.bmi_highest_cop,
           ))

# Check
dat %>%
  freq(bmi_highest_dem)

dat %>%
  filter(is.na(bmi_highest_dem)) %>%
  freq(dem.bmi_highest)

dat %>%
  filter(is.na(bmi_highest_dem)) %>%
  freq(dem.bmi_highest_cop)
```

## BMI signup
```{r bmi highest create variables based on data available}
dat <- dat %>%
  mutate(bmi_signup_dem =
           case_when(
             !is.na(dem.bmi_signup) ~ dem.bmi_signup,
             !is.na(dem.bmi_signup_cop) ~ dem.bmi_signup_cop,
           ))

# Check
dat %>%
  descr(dem.bmi_signup)

dat %>%
  filter(is.na(bmi_signup_dem)) %>%
  freq(dem.bmi_signup)

dat %>%
  filter(is.na(bmi_signup_dem)) %>%
  freq(dem.bmi_signup_cop)
```

## Highest education
```{r highest education create variables based on data available}
dat <- dat %>%
  mutate(highest_education =
           case_when(
             !is.na(dem.highest_education_collapsed) ~ dem.highest_education_collapsed,
             !is.na(employ.highest_education_collapsed_cop) ~ employ.highest_education_collapsed_cop,
           ))

# Check
dat %>%
  freq(highest_education)

dat %>%
  filter(is.na(highest_education)) %>%
  freq(dem.highest_education_collapsed)

dat %>%
  filter(is.na(highest_education)) %>%
  freq(employ.highest_education_collapsed_cop)

24.26+50.04
```

# Merge excluded data with analysis data
```{r merge excluded data with analysis data}
excl_dat <- dat %>%
  select(ID,
         excluded,
         age_dem,
         sex_final,
         racially_minoritised,
         highest_education,
         bmi_lowest_dem,
         bmi_highest_dem,
         bmi_signup_dem)

dat_merged <- excl_dat %>%
  bind_rows(symptom_dat)
```

```{r create AS levels or higher variable}
# Create A levels or higher variable
dat_merged <- dat_merged %>%
  mutate(AS_Levels_higher =
           case_when(highest_education == "None of the above"  |
                       highest_education == "GCSEs/CSEs/O-levels or equivalent"  |
                       highest_education == "NVQ/HND/HNC or equivalent"  ~ "No",
                    
                     highest_education == "A-levels/AS-levels or equivalent" |
                       highest_education == "University" ~ "Yes"
                    )
         )

# check
dat_merged %>%
  freq(AS_Levels_higher)
```
# COMPARISONS
## Categorical variables
```{r create non-numeric variable for excluded}
dat_merged <- dat_merged %>%
  mutate(excluded_factor =
           case_when(excluded == 1 ~ "Yes",
                     excluded == 0 ~ "No"))
```

```{r list categorical dummy variables symptom}
descriptives.columns <- c(
  "excluded",
         "sex_final",
         "racially_minoritised",
         "AS_Levels_higher"
)

descriptives.columns.dummy <- c(
         "sex_final",
         "racially_minoritised",
         "AS_Levels_higher"
)
```

Dummy coding for categorical variables
```{r dummy coding categorical variables symptom}
# Create dataset
descriptives_df <- dat_merged %>%
  select(descriptives.columns)

# Dummy coding
descriptives_dummy <- fastDummies::dummy_cols(descriptives_df,
                                              select_columns = descriptives.columns.dummy
                                              )
# Check
colnames(descriptives_dummy)
```

## Being female
```{r chi-squared sex}
dat_merged %>%
  group_by(excluded) %>%
  freq(sex_final)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$sex_final_Female ~ descriptives_dummy$excluded ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")


test$p.value
```

# AS levels or higher
```{r chi-squared AS levels or higher}
dat_merged %>%
  group_by(excluded) %>%
  freq(AS_Levels_higher)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$AS_Levels_higher_Yes ~ descriptives_dummy$excluded ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")


test$p.value
```

# Racially minoritised
```{r chi-squared racially minoritised}
dat_merged %>%
  group_by(excluded) %>%
  freq(racially_minoritised)

test <-RVAideMemoire::chisq.bintest(descriptives_dummy$racially_minoritised_Yes ~ descriptives_dummy$excluded ,
                                     alpha = 0.001,
                             correct = F,
                             p.method ="fdr")


test$p.value
```
# Continuous variables
## Generate mode function
```{r mode function symptom}
mode_func <- function(x, na.rm = FALSE) {
  if(na.rm){
    x = x[!is.na(x)]
  }

  ux <- unique(x)
  return(ux[which.max(tabulate(match(x, ux)))])
}
```

## Table: Comparison of continuous variables
```{r table compare continuous variables symptom}
# Create table
numeric_table <- dat_merged %>% 
  group_by(excluded) %>%
  summarise_at(vars(age_dem,
                    bmi_signup_dem,
                    bmi_lowest_dem,
                    bmi_highest_dem),
    .funs =
      list(
       # ~mean(., na.rm = T),
       # ~sd(., na.rm = T),
        ~IQR(., na.rm=T),
      #  mode = ~mode_func(., na.rm = T),
        ~median(., na.rm = T)
      #  ~min(., na.rm = T),
      #  ~max(., na.rm = T),
      #  missing = ~skimr::n_missing(.),
      #  ~skew(., na.rm = T),
      #  kurtosis = ~kurtosi(., na.rm = T)
      )
  )

numeric_table
```

```{r checking normality}
# Age
ggpubr::ggqqplot(dat_merged,
         "age_dem",
         facet.by = "excluded")

dat_merged %>%
  filter(excluded == 1) %>%
  ggplot(mapping = aes(x = age_dem)) +
  geom_histogram() +
  theme_minimal() +
  ggtitle("Histogram of age in excluded participants") +
  xlab("Age")

# BMI lowest
ggpubr::ggqqplot(dat_merged,
         "bmi_lowest_dem",
         facet.by = "excluded")

dat_merged %>%
  filter(excluded == 1) %>%
  ggplot(mapping = aes(x = bmi_lowest_dem)) +
  geom_histogram() +
  theme_minimal() +
  ggtitle("Histogram of lowest BMI in excluded participants") +
  xlab("Lowest BMI")

# BMI highest
ggpubr::ggqqplot(dat_merged,
         "bmi_highest_dem",
         facet.by = "excluded")

dat_merged %>%
  filter(excluded == 1) %>%
  ggplot(mapping = aes(x = bmi_highest_dem)) +
  geom_histogram() +
  theme_minimal() +
  ggtitle("Histogram of highest BMI in excluded participants") +
  xlab("Highest BMI")

# BMI signup
ggpubr::ggqqplot(dat_merged,
         "bmi_signup_dem",
         facet.by = "excluded")

dat_merged %>%
  filter(excluded == 1) %>%
  ggplot(mapping = aes(x = bmi_signup_dem)) +
  geom_histogram() +
  theme_minimal() +
  ggtitle("Histogram of signup BMI in excluded participants") +
  xlab("Signup BMI")
```

## Age 
Testing homoscedasticity: Levene’s test
```{r check homoscedasticity of age}
car::leveneTest(age_dem ~ excluded_factor,
                data = dat_merged) 
```

Both assumptions violated; so performed the non-parametric equivalent of t-test: Mann-Whitney
```{r independent 2-group Mann-Whitney U test age }
age_wilcox <- wilcox.test(dat_merged$age_dem ~ dat_merged$excluded_factor,
            correct = FALSE,
            exact = FALSE,
            p.adjust.methods = "fdr")

age_wilcox$p.value
print(age_wilcox)
```
## BMI lowest
Testing homoscedasticity: Levene’s test
```{r check homoscedasticity of lowest bmi}
car::leveneTest(bmi_lowest_dem ~ excluded_factor,
                data = dat_merged) 
```

Both assumptions violated; so performed the non-parametric equivalent of t-test: Mann-Whitney
```{r independent 2-group Mann-Whitney U test bmi_lowest_dem }
bmi_lowest_dem_wilcox <- wilcox.test(dat_merged$bmi_lowest_dem ~ dat_merged$excluded_factor,
            correct = FALSE,
            exact = FALSE,
            p.adjust.methods = "fdr")

bmi_lowest_dem_wilcox$p.value
print(bmi_lowest_dem_wilcox)
```
## BMI highest
Testing homoscedasticity: Levene’s test
```{r check homoscedasticity of highest bmi}
car::leveneTest(bmi_highest_dem ~ excluded_factor,
                data = dat_merged) 
```

Both assumptions violated; so performed the non-parametric equivalent of t-test: Mann-Whitney
```{r independent 2-group Mann-Whitney U test bmi_highest_dem }
bmi_highest_dem_wilcox <- wilcox.test(dat_merged$bmi_highest_dem ~ dat_merged$excluded_factor,
            correct = FALSE,
            exact = FALSE,
            p.adjust.methods = "fdr")

bmi_highest_dem_wilcox$p.value
print(bmi_highest_dem_wilcox)
```

## BMI signup
Testing homoscedasticity: Levene’s test
```{r check homoscedasticity of signup bmi}
car::leveneTest(bmi_signup_dem ~ excluded_factor,
                data = dat_merged) 
```

Both assumptions violated; so performed the non-parametric equivalent of t-test: Mann-Whitney
```{r independent 2-group Mann-Whitney U test bmi_signup_dem }
bmi_signup_dem_wilcox <- wilcox.test(dat_merged$bmi_signup_dem ~ dat_merged$excluded_factor,
            correct = FALSE,
            exact = FALSE,
            p.adjust.methods = "fdr")

bmi_signup_dem_wilcox$p.value
print(bmi_signup_dem_wilcox)
```