---
title: 'Sensitivity analysis: BE no loss control'
author: "Helena Davies"
date: "17/12/2021"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to data channel
```{r Read in file with path to data channel on teams}
source(file = "../../credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = paste0(filepath_functions, "add_numeric.R"))
source(file = paste0(filepath_functions, "remove_duplicates.R"))
source(file = paste0(filepath_functions, "package_check.R"))
source("./functions.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools",
              "sjlabelled",
              "Amelia",
              "gtsummary",
              "janitor",
              "psych",
              "corrplot",
              "rstatix",
              "networktools",
              "nnet",
              "bootnet",
              "caret",
              "Matrix",
              "qgraph",
              "NetworkComparisonTest",
              "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

# Read in merged data with variables created
Read in data 
```{r Read in data}
# Symptom dat
symptom_dat <- readRDS(file = "../data/symptom_dat_analysis2022-01-13.rds")
dim(symptom_dat)
colnames(symptom_dat)

# Select and rename variables
symptom_dat <- symptom_dat %>%
  select(
    ID,
    age = age_sx_level,
    sex = sex_final,
    sex_numeric = sex_final_numeric,
    ethnicity,
    bmi_signup = bmi_signup_sx_level,
    bmi_lowest =bmi_lowest_sx_level,
    bmi_highest = bmi_highest_sx_level,
    more_hyperactivity = more_hyperactivity_sx_level,
    more_irritability= more_irritability_sx_level,
    more_self_confidence = more_self_confidence_sx_level,
    less_sleep = less_sleep_sx_level,                    
    more_talkative = more_talkative_sx_level,
    racing_thoughts = racing_thoughts_sx_level,
    conc_difficulties = conc_difficulties_sx_level,     
    more_energy = more_energy_sx_level,
    more_active = more_active_sx_level,
    more_social = more_social_sx_level,             
    higher_libido = higher_libido_sx_level,
    more_risky_beh = more_risky_beh_sx_level,
    reckless_spending = reckless_spending_sx_level,
   
    more_hyperactivity_numeric = more_hyperactivity_numeric_sx_level,
   more_irritability_numeric= more_irritability_numeric_sx_level,
   more_self_confidence_numeric = more_self_confidence_numeric_sx_level,
   less_sleep_numeric = less_sleep_numeric_sx_level,                    
   more_talkative_numeric = more_talkative_numeric_sx_level,
   racing_thoughts_numeric = racing_thoughts_numeric_sx_level,
   conc_difficulties_numeric = conc_difficulties_numeric_sx_level,     
   more_energy_numeric = more_energy_numeric_sx_level,
   more_active_numeric = more_active_numeric_sx_level,
   more_social_numeric = more_social_numeric_sx_level,             
   higher_libido_numeric = higher_libido_numeric_sx_level,
   more_risky_beh_numeric = more_risky_beh_numeric_sx_level,
   reckless_spending_numeric = reckless_spending_numeric_sx_level,
   
   binge_eating_with_loss_control,
   binge_eating_with_loss_control_numeric
    ) 
```

```{r create binge no loss control dataset}
mania_nodes_BE_no_loss_control <- symptom_dat %>%
   filter(binge_eating_with_loss_control == "BE no loss control") %>%
  select(
   more_hyperactivity_numeric,
   more_irritability_numeric,
   more_self_confidence_numeric,
   less_sleep_numeric,                    
   more_talkative_numeric,
   racing_thoughts_numeric,
   conc_difficulties_numeric,     
   more_energy_numeric,
   more_active_numeric,
   more_social_numeric,             
   higher_libido_numeric,
   more_risky_beh_numeric,
   reckless_spending_numeric,
   sex_numeric,
   age
  )
```

### Abbreviations of symptoms 
```{r abbreviations of symptoms }
shortnames <- c(
  "hyp",
                "irr",
                "scf",
                "sle",
                "talk",
                "rac",
                "con",
                "ene",
                "act",
                "soc",
                "lib",
                "ris",
                "mon",
                "sex",
                "age")
```

### Long names 
```{r nodes long names }
longnames <- c(
  "Hyperactivity",
  "More irritability",
  "More self-confidence",
  "Less sleep",
  "More talkative",
  "Racing thoughts",
  "Concentration difficulties",
  "More energy",
  "More active",
  "More social",
  "Higher libido",
  "Unusual and/or risky behaviour",
  "Reckless spending",
  "Sex",
  "Age"
  )
```

# BE no loss control network
### Generate initial network for use in generating predictability estimates BE_no_loss_control
```{r initial network for use in predictability BE_no_loss_control}
# Type of variable. C = categorical, g = gaussian
type = c(rep("c", 14),
         "g")

# Number of levels. For the first 14 variables, there are 2 levels (0 and 1). The last variable (age) is continuous so level is set to 1.
level = c(rep(2, 14), 
          1) 

BE_no_loss_control_network <- mgm::mgm(mania_nodes_BE_no_loss_control,
                  type = type,
                  level = level,
                  lambdaSel = "EBIC",
                  lambdaGam = 0.25,
                  binarySign = TRUE, 
                  scale = TRUE)
```

### Adding predictability of nodes BE_no_loss_control
From this paper: https://link.springer.com/article/10.3758/s13428-017-0910-x
```{r generating predictability of nodes BE_no_loss_control}
p_obj <- predict(object = BE_no_loss_control_network,
                 data = mania_nodes_BE_no_loss_control,
                 errorCat = c("CC", "nCC", "CCmarg"),
                 errorCon = c("R2"))

p_obj$error

# To display both the accuracy of the intercept model and the normalized accuracy (contribution by other variables), we require a list for the ring-segments and a list for the corresponding colors:

error_list_BE_no_loss_control <- list() # List for ring segments
beyondmarg <- vector()

for(i in 1:14) beyondmarg[[i]] <- p_obj$errors[i, 3]-p_obj$errors[i, 5]
for(i in 1:14) error_list_BE_no_loss_control[[i]] <- c(p_obj$errors[i, 5], beyondmarg[[i]])
error_list_BE_no_loss_control[[15]] <- p_obj$errors[15,2]

color_list <- list() # List for colours
for(i in 1:14) color_list[[i]] <- c("#ffa500", "#ff4300")
#color_list[[15]] <- p_obj$errors[15,2]
color_list[[15]] <- "#90B4D4"
```

### Walktrap algorithm: 
https://www.nature.com/articles/srep05918
https://pure.uva.nl/ws/files/21235882/Network_Analysis_on_Attitudes.png
Walktrap, developed by Pascal Pons, is an algorithm in graph theory, used to identify communities in large networks via random walks. These random walks are then used to compute distances between nodes. Nodes are then assigned into groups with small intra and larger inter-community distances via bottom-up hierarchical clustering. It should be noted, of course, that this algorithm considers only one community per node, which in some cases can be an incorrect hypothesis.
```{r walktrap algorithm BE_no_loss_control}
# Create an igraph object containing the information on the  network and take the absolute values of the edge weights because the walktrap algorithm can only deal with positive edge values
BE_no_loss_control_network <- estimateNetwork(mania_nodes_BE_no_loss_control,
                               default = "mgm",
                               type = type,
                               level = level,
                               tuning = 0.25,
                               binarySign = TRUE)


BE_no_loss_controligraph <- igraph::graph_from_adjacency_matrix(abs(BE_no_loss_control_network$graph), 
                                      weighted =TRUE,
                                      add.colnames = FALSE)


# Run walktrap algorithm on the network 
BE_no_loss_controlCom <- igraph::cluster_walktrap(BE_no_loss_controligraph)

# Extract the found communities using the following command:
BE_no_loss_controlcommunities <- igraph::communities(BE_no_loss_controlCom)

# Manually move age and sex into their own community (they are covariates. We estimated the groups first because we need the associations that have been adjusted for age and sex, but do not want them to form part of a group because they are not symptoms)
BE_no_loss_controlcommunities$`2` <- c(1,
                                       2,
                                       4,
                                       5,
                                       6,
                                       7,
                                       12, 
                                       13)

BE_no_loss_controlcommunities$`3`  <- c(14,
                                       15)

# Rename clusters
BE_no_loss_controlcommunities$`Cluster 1` <- BE_no_loss_controlcommunities$`1` 
BE_no_loss_controlcommunities$`1`  <- NULL

BE_no_loss_controlcommunities$`Cluster 2` <- BE_no_loss_controlcommunities$`2` 
BE_no_loss_controlcommunities$`2`  <- NULL

BE_no_loss_controlcommunities$`Covariates` <- BE_no_loss_controlcommunities$`3` 
BE_no_loss_controlcommunities$`3`  <- NULL
```

### Plot BE_no_loss_control network with walktrap algorithm AND predictability of nodes 
Using mgm package
```{r plotting BE_no_loss_control network with walktrap and predictability}
# Type of variable. C = categorical, g = gaussian
type = c(rep("c", 14),
         "g")

# Number of levels. For the first 14 variables, there are 2 levels (0 and 1). The last variable (age) is continuous so level is set to 1.
level = c(rep(2, 14), 
          1) 

BE_no_loss_control_network <- mgm::mgm(mania_nodes_BE_no_loss_control,
                  type = type,
                  level = level,
                  lambdaSel = "EBIC",
                  lambdaGam = 0.25,
                  binarySign = TRUE, 
                  scale = TRUE)

BE_no_loss_control_network_plot <- qgraph::qgraph(BE_no_loss_control_network$pairwise$wadj, # weighted adjacency matrix as input
       #layout = layout, 
       pie = error_list_BE_no_loss_control, # provide errors as input
       pieColor = color_list,
       edge.color = "blue3",
       cut = 0, 
       labels = shortnames,
       nodeNames = longnames,
       groups =  BE_no_loss_controlcommunities,
       palette = "colorblind",
       label.scale = T,
       title = "Sensitivity: Network of mania symptoms in BE no loss of control sample,
                   n = 926"
      )
```

### Plot using the bootnet package for use in later analyses (e.g., centrality estimates, etc)
```{r plotting network using estimateNetwork BE_no_loss_control}
BE_no_loss_control_network_bootnet <- estimateNetwork(mania_nodes_BE_no_loss_control,
                               default = "mgm",
                               type = type,
                               level = level,
                               tuning = 0.25,
                               binarySign = TRUE,
                               criterion = "EBIC",
                               labels = shortnames)


BE_no_loss_control_network_bootnet_plot <- plot(BE_no_loss_control_network_bootnet,
                           layout = "spring",
                           labels = shortnames, 
                           nodeNames = longnames,
                           legend = TRUE,
                           title = paste("Sensitivity: Symptom network of mania items in BE no loss control sample,
                   n =", BE_no_loss_control_network_bootnet$nPerson))
```

### BE_no_loss_control network information
```{r BE_no_loss_control network information BE_no_loss_control}
BE_no_loss_control_network_bootnet$graph # the weights (adjacency) matrix of the network (symmetrical in undirected networks)
BE_no_loss_control_network_bootnet$intercepts # the thresholds (represent the intercept for each symptom in the regularized logistic regression analyses used to estimate the networks)
BE_no_loss_control_network_bootnet$results # weights matrix and intercepts
BE_no_loss_control_network_bootnet$labels # variable labels
BE_no_loss_control_network_bootnet$nNodes # number of nodes in network
BE_no_loss_control_network_bootnet$nPerson # number of persons in network
```

### BE_no_loss_control centrality estimates
```{r centrality estimates BE_no_loss_control}
# Raw centrality measures (not standardised)
qgraph::centrality(BE_no_loss_control_network_bootnet)

# Standardised centrality estimates [node strength]
plot(qgraph::centrality(BE_no_loss_control_network_bootnet)$InDegree,
     type = "b") 

# Standardised centrality estimated for four centrality indices
qgraph::centralityTable(BE_no_loss_control_network_bootnet,
                        labels = longnames)

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_centrality_plot_BE_no_loss_control.png")) 

qgraph::centralityPlot(BE_no_loss_control_network_bootnet,
               include ="all",
               labels = longnames) 

dev.off()
```

### BE_no_loss_control Edge weight accuracy
Use the bootnet() function to estimate edge weight accuracy and centrality stability and plot them
See: Estimating psychological networks and their accuracy: A tutorial paper
Bootstrapping = picking people with replacement, i.e. each sample will have a different composition of people (e.g. choosing a random 70% of the sample each time)
```{r edge weight accuracy BE_no_loss_control network}
edge_accuracy_BE_no_loss_control_network <- bootnet(BE_no_loss_control_network_bootnet,
                                     nBoots = 1000, 
                                     nCores = 4,
                                     statistics = c("edge", 
                                                    "strength",
                                                    "betweenness",
                                                    "closeness",
                                                    "expectedInfluence"),
                                     labels = shortnames
                                     ) 

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_edge_accuracy_plot_BE_no_loss_control.png")) 

plot(edge_accuracy_BE_no_loss_control_network,
                                      #plot = "interval",
                                      # split0 = TRUE,
                                      order = "sample",
                                       labels = TRUE)

dev.off()

edge_accuracy_BE_no_loss_control_network_plot <- plot(edge_accuracy_BE_no_loss_control_network,
                                      #plot = "interval",
                                      # split0 = TRUE,
                                      order = "sample",
                                       labels = TRUE)

dev.off()

edge_accuracy_BE_no_loss_control_network_plot
```

### BE_no_loss_control centrality accuracy
```{r centrality accuracy BE_no_loss_control network}
centrality_stability_BE_no_loss_control_network <- bootnet(BE_no_loss_control_network_bootnet,
                                nBoots = 1000, 
                                nCores = 1,
                                type = "case", #case-dropping bootstrap
                                statistics = c("closeness",
                                               "strength",
                                               "betweenness",
                                               "expectedInfluence")) 

centrality_stability_BE_no_loss_control_network

# Table of all statistics from original sample 
centrality_stability_BE_no_loss_control_network$sampleTable 

# Results of bootstrap
centrality_stability_BE_no_loss_control_network$boots

# Table of all statistics from bootstraps
centrality_stability_BE_no_loss_control_network$bootTable

# Plot centrality stability
png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_centrality_stability_plot_BE_no_loss_control.png")) 

plot(centrality_stability_BE_no_loss_control_network,
     statistics = c("closeness",
                    "strength",
                    "betweenness",
                    "expectedInfluence"))

dev.off()

centrality_stability_BE_no_loss_control_network_plot <- plot(centrality_stability_BE_no_loss_control_network,
                                                statistics = c("closeness",
                                                             "strength",
                                                             "betweenness",
                                                             "expectedInfluence"))
centrality_stability_BE_no_loss_control_network_plot


# CS-coefficient (to quantify the centrality stability)
corStability(centrality_stability_BE_no_loss_control_network,
              cor = 0.7,
              statistics = "all")
```

### Test significance of differences (between edge weights and node centralities) to test for differences within a single network 
Significance: Specific edge weights 
```{r test significance of differences of specific edge weight BE_no_loss_control network}
# Plot significant differences (alpha = 0.05) of edge weights:
png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_sig_diff_edges_plot_BE_no_loss_control.png")) 

plot(edge_accuracy_BE_no_loss_control_network,
     "edge",
     plot = "difference",
     onlyNonZero = TRUE,
     order = "sample",
     labels = TRUE
     )

dev.off()
```

Significance: Node centralities
```{r test significance of differences of node centralities BE_no_loss_control network}
# Plot significant differences (alpha = 0.05) of node centrality eg. strength for all nodes:
png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_sig_diff_centrality_plot_BE_no_loss_control.png")) 

plot(edge_accuracy_BE_no_loss_control_network,
     "expectedInfluence",
     plot = "difference",
     order = "sample"
     ) # Note: use edge accuracy estimates for this as centrality is a measure of connecting edges

dev.off()
# Test for difference in strength between specific nodes - perhaps more useful if you have apriori reason to explore specific differents in nodes
# Eg. difference in centrality between ene and expectedInfluence for strength 
# differenceTest(edge_accuracy_ED_network,  "ene", "rac", "expectedInfluence")
```

### Average layout
```{r load other networks}
load(paste0(filepath_own, "NetAnalEDMan/scripts/MainAnalysis_environment.RData"))
```

Calculate average layout of 3 networks to then constrain them all to that layout (don't use Fruchterman-Reingold)
```{r calculating average layout symptom data}
sens_average_layout <- qgraph::averageLayout(BE_network_plot,
                                        BE_no_loss_control_network_plot,
                                        no_BE_network_plot
                                        )
```

Re-plot each using 'average_layout'
```{r re-plot each using average layout symptom data}
# BE no loss control
BE_no_loss_control_network_plot <- qgraph::qgraph(BE_no_loss_control_network$pairwise$wadj, # weighted adjacency matrix as input
       layout = sens_average_layout, 
       pie = error_list_BE_no_loss_control, # provide errors as input
       pieColor = color_list,
       edge.color = "blue3",
       cut = 0, 
       labels = shortnames,
       nodeNames = longnames,
       groups =  BE_no_loss_controlcommunities,
       palette = "colorblind",
       color = c("orange",
                 "light blue",
                 "grey" # covariates in grey
                 ),
       label.scale = T,
       title = "Sens analysis: Network of mania symptoms in BE no loss control sample,
                   n = 926",
       filetype = "png",
       filename = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_network_BE_no_loss_control_average_layout"),
       width = 10,
       height = 10
      )

# BE loss control
BE_loss_control_network_plot <- qgraph::qgraph(BE_network$pairwise$wadj, # weighted adjacency matrix as input
       layout = sens_average_layout, 
       pie = error_list_BE, # provide errors as input
       pieColor = color_list,
       edge.color = "blue3",
       cut = 0, 
       labels = shortnames,
       nodeNames = longnames,
       groups =  BEcommunities,
       palette = "colorblind",
       color = c("orange",
                 "light blue",
                  "red",
                 "grey" # covariates in grey
                 ),
       label.scale = T,
       title = "Sens analysis: Network of mania symptoms in BE sample,
                   n = 12104",
       filetype = "png",
       filename = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_network_BE_average_layout"),
       width = 10,
       height = 10
      )

# No BE 
no_BE_network_plot <- qgraph::qgraph(no_BE_network$pairwise$wadj, # weighted adjacency matrix as input
       layout = sens_average_layout, 
       pie = error_list_no_BE, # provide errors as input
       pieColor = color_list,
       edge.color = "blue3",
       cut = 0, 
       labels = shortnames,
       nodeNames = longnames,
       groups =  no_BEcommunities,
       palette = "colorblind",
       color = c("orange",
                 "light blue",
                
                 "grey" # covariates in grey
                 ),
       label.scale = T,
       title = "Network of mania symptoms in no BE sample,
                   n = 22,122",
       filetype = "png",
       filename = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/sens_network_no_BE_average_layout"),
       width = 10,
       height = 10
      )
```

# SYMPTOM LEVEL- COMPARING NETWORKS
## BE vs BE no loss of contorl 
### 1. Correlation of the weighted adjacency matrix of both models: Age and sex included versus not
```{r BE vs BE no loss control correlation of weighted adjacency matrices}
# Drop age and sex from adjacency matrices
BE_network_no_age_sex <- tril(BE_network_bootnet$graph) 
BE_network_no_age_sex <- BE_network_no_age_sex[-c(14,15),-c(14,15)]
diag(BE_network_no_age_sex) <- NA_real_
BE_network_no_age_sex <- as.vector(BE_network_no_age_sex)

BE_no_loss_control_network_no_age_sex <- tril(BE_no_loss_control_network_bootnet$graph) 
BE_no_loss_control_network_no_age_sex <- BE_no_loss_control_network_no_age_sex[-c(14,15),-c(14,15)]
diag(BE_no_loss_control_network_no_age_sex) <- NA_real_
BE_no_loss_control_network_no_age_sex <- as.vector(BE_no_loss_control_network_no_age_sex)

corr_no_age_sex <- cor.test(x=BE_network_no_age_sex,
                 y=BE_no_loss_control_network_no_age_sex,
                 method = 'spearman')

corr_no_age_sex # 0.9
corr_no_age_sex$p.value # 2.258412e-60
```

### 2. Absolute sum of adjacency matrices for the two networks [edge weights]
```{r BE vs BE no loss control absolute sum of adjacency matrices}
sum(abs(na.omit(BE_network_no_age_sex))) 
sum(abs(na.omit(BE_no_loss_control_network_no_age_sex)))
```

### 3. Compare centrality
NB: Tried to remove age + sex using the below code. But then the standardised plot changes the centrality indices (either due to labelling errors or standardisation errors influenced by the number of nodes)

BE_network_bootnet_no_age_sex_graph <- BE_network_bootnet$graph[-c(14,15),-c(14,15)]
BE_no_loss_control_network_bootnet_no_age_sex_graph <- BE_no_loss_control_network_bootnet$graph[-c(14,15),-c(14,15)]
```{r BE vs BE no loss control compare centrality}
# Plot centrality differences
BE_vs_BE_no_loss_control_centrality_plot <- centralityPlot(list( "Binge eating" = BE_network_bootnet,
               "Binge eating no loss of control" = BE_no_loss_control_network_bootnet),
               include = "ExpectedInfluence",
               orderBy = "ExpectedInfluence",
               labels = longnames)

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/centrality_diff_BE_vs_BE_no_loss_control.png"))

BE_vs_BE_no_loss_control_centrality_plot + labs(x = "Centrality indices",
            y = "Nodes",
            colour = "Comparison group")

dev.off()
```

### 4. Compare networks using the Network Comparison Test
```{r BE vs BE no loss control compare centrality Network Comparison Test}
# Use output from estimatenetwork as data, that way specific settings eg. model and tuning are retained
networkcomparison_BE_v_BE_no_loss_control <- NCT(BE_network_bootnet,
                         BE_no_loss_control_network_bootnet,
                         it = 1000, 
                         test.edges = T,
                         edges=list(c(1,2), # List all edges other than age and sex
                                    c(1,3),
                                    c(1,4),
                                    c(1,5),
                                    c(1,6),
                                    c(1,7),
                                    c(1,8),
                                    c(1,9),
                                    c(1,10),
                                    c(1,11),
                                    c(1,12),
                                    c(1,13),
           
                                    c(2,3),
                                    c(2,4),
                                    c(2,5),
                                    c(2,6),
                                    c(2,7),
                                    c(2,8),
                                    c(2,9),
                                    c(2,10),
                                    c(2,11),
                                    c(2,12),
                                    c(2,13),
           
                                    c(3,4),
                                    c(3,5),
                                    c(3,6),
                                    c(3,7),
                                    c(3,8),
                                    c(3,9),
                                    c(3,10),
                                    c(3,11),
                                    c(3,12),
                                    c(3,13),
           
                                    c(4,5),
                                    c(4,6),
                                    c(4,7),
                                    c(4,8),
                                    c(4,9),
                                    c(4,10),
                                    c(4,11),
                                    c(4,12),
                                    c(4,13),
                                    
                                    c(5,6),
                                    c(5,7),
                                    c(5,8),
                                    c(5,9),
                                    c(5,10),
                                    c(5,11),
                                    c(5,12),
                                    c(5,13),
          
          
                                    c(6,7),
                                    c(6,8),
                                    c(6,9),
                                    c(6,10),
                                    c(6,11),
                                    c(6,12),
                                    c(6,13),
           
                                    c(7,8),
                                    c(7,9),
                                    c(7,10),
                                    c(7,11),
                                    c(7,12),
                                    c(7,13),
           
                                    c(8,9),
                                    c(8,10),
                                    c(8,11),
                                    c(8,12),
                                    c(8,13),
          
                                    c(9,10),
                                    c(9,11),
                                    c(9,12),
                                    c(9,13),
           
                                    c(10,11),
                                    c(10,12),
                                    c(10,13),
           
                                    c(11,12),
                                    c(11,13),
                                    
                                    c(12,13)
                         ), 
           
                         test.centrality = TRUE,
                         centrality = c("closeness",
                                        "betweenness",
                                        "strength",
                                        "expectedInfluence"),
                         nodes = 1:13, # List all nodes other than age and sex
                         p.adjust.methods = "bonferroni"
                         )

networkcomparison_BE_v_BE_no_loss_control
```

### 5. Global strength: BE vs BE no loss control differences  
```{r BE vs BE no loss control Network Comparison Test results - global strength}
networkcomparison_BE_v_BE_no_loss_control$glstrinv.sep # global strength of each network - adding up all the networks in each network, is there a difference?
networkcomparison_BE_v_BE_no_loss_control$glstrinv.real # difference in global strength
networkcomparison_BE_v_BE_no_loss_control$glstrinv.pval # significance of difference in global strength

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/global_strength_plot_BE_vs_BE_no_loss_control.png")) 

plot(networkcomparison_BE_v_BE_no_loss_control, what = "strength") # the results of the global strength test can be plotted

dev.off()
```

### 6. Network structure: BE vs BE no loss control differences 
Results can also be plotted. The permutation test results in a reference distribution of test statistics under the relevant null hypothesis. NCT is accompanied by a plotting function to visualizethe results. The red triangle indicates the test statistics based on the observed (real) data.
IF 0, just say p < 0.001
```{r BE vs BE no loss control Network Comparison Test results - network structure}
networkcomparison_BE_v_BE_no_loss_control$nwinv.real # max difference in network structure
networkcomparison_BE_v_BE_no_loss_control$nwinv.pval # significance of difference in structure/organisation

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/network_structure_plot_BE_vs_BE_no_loss_control.png")) 

plot(networkcomparison_BE_v_BE_no_loss_control, # the results of the network structure test can be plotted
     what = "network")

dev.off()
```

### 6a. If significant - SPECIFIC EDGE WEIGHT DIFFERENCES 
NB: When writing up, will need to refer back to the networks to see which edge weight was stronger and in which model. This only tells you if the difference was significant, not in which direction.
```{r BE vs BE no loss control Network Comparison Test results - specific edge weights}
networkcomparison_BE_v_BE_no_loss_control$einv.real # difference in edge weights of OBSERVED networks
networkcomparison_BE_v_BE_no_loss_control$einv.pvals # The Holm-Bonferroni corrected p values per edge from the permutation test concerning differences in edges weight
networkcomparison_BE_v_BE_no_loss_control$einv.perm # The values of the difference in edge weight of the permuted networks. Only iftest.edges =TRUE 
# plot(networkcomparison_ANBP_BN, # The distribution(s) of the edge strength invariance test can be plotted
 #    what="edge")

edge_accuracy_BE_no_loss_control_network$sampleTable # 0.53483441	# 0.50712811	# 1.74399732 # 0.58691867	
edge_accuracy_BE_network$sampleTable # 0.311661625	# 0.208428875	# 1.268862060		# 0.221296324	# 0.221296324
```

### 7. Significant centrality differences
```{r BE vs BE no loss control Network Comparison Test results - significant differences centrality}
networkcomparison_BE_v_BE_no_loss_control$diffcen.real # The values of the difference in centralities of the OBSERVED networks. 
networkcomparison_BE_v_BE_no_loss_control$diffcen.perm # The values of the difference in centralities of the PERMUTED networks. 
networkcomparison_BE_v_BE_no_loss_control$diffcen.pval # p-values (corrected for multiple testing or not according to ’p.adjust.methods’) per node from the permutation test concerning differences in centralities. 
```

## No BE vs BE no loss of contorl 
### 1. Correlation of the weighted adjacency matrix of both models
```{r No BE vs BE no loss control correlation of weighted adjacency matrices}
# Drop age and sex from adjacency matrices
no_BE_network_no_age_sex <- tril(no_BE_network_bootnet$graph) 
no_BE_network_no_age_sex <- no_BE_network_no_age_sex[-c(14,15),-c(14,15)]
diag(no_BE_network_no_age_sex) <- NA_real_
no_BE_network_no_age_sex <- as.vector(no_BE_network_no_age_sex)

BE_no_loss_control_network_no_age_sex <- tril(BE_no_loss_control_network_bootnet$graph) 
BE_no_loss_control_network_no_age_sex <- BE_no_loss_control_network_no_age_sex[-c(14,15),-c(14,15)]
diag(BE_no_loss_control_network_no_age_sex) <- NA_real_
BE_no_loss_control_network_no_age_sex <- as.vector(BE_no_loss_control_network_no_age_sex)

corr_no_age_sex <- cor.test(x=no_BE_network_no_age_sex,
                 y=BE_no_loss_control_network_no_age_sex,
                 method = 'spearman')

corr_no_age_sex # 0.9
corr_no_age_sex$p.value # 2.258412e-60
```

### 2. Absolute sum of adjacency matrices for the two networks [edge weights]
```{r No BE vs BE no loss control absolute sum of adjacency matrices}
sum(abs(na.omit(no_BE_network_no_age_sex))) 
sum(abs(na.omit(BE_no_loss_control_network_no_age_sex)))
```

### 3. Compare centrality
```{r No BE vs BE no loss control compare centrality}
# Plot centrality differences
no_BE_vs_BE_no_loss_control_centrality_plot <- centralityPlot(list( "No binge eating" = no_BE_network_bootnet,
               "Binge eating no loss of control" = BE_no_loss_control_network_bootnet),
               include = "ExpectedInfluence",
               orderBy = "ExpectedInfluence",
               labels = longnames)

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/centrality_diff_no_BE_vs_BE_no_loss_control.png"))

no_BE_vs_BE_no_loss_control_centrality_plot + labs(x = "Centrality indices",
            y = "Nodes",
            colour = "Comparison group")

dev.off()
```

### 4. Compare networks using the Network Comparison Test
```{r No BE vs BE no loss control compare centrality Network Comparison Test}
# Use output from estimatenetwork as data, that way specific settings eg. model and tuning are retained
networkcomparison_no_BE_v_BE_no_loss_control <- NCT(no_BE_network_bootnet,
                         BE_no_loss_control_network_bootnet,
                         it = 1000,
                         test.edges = T,
                         edges=list(c(1,2), # List all edges other than age and sex
                                    c(1,3),
                                    c(1,4),
                                    c(1,5),
                                    c(1,6),
                                    c(1,7),
                                    c(1,8),
                                    c(1,9),
                                    c(1,10),
                                    c(1,11),
                                    c(1,12),
                                    c(1,13),
           
                                    c(2,3),
                                    c(2,4),
                                    c(2,5),
                                    c(2,6),
                                    c(2,7),
                                    c(2,8),
                                    c(2,9),
                                    c(2,10),
                                    c(2,11),
                                    c(2,12),
                                    c(2,13),
           
                                    c(3,4),
                                    c(3,5),
                                    c(3,6),
                                    c(3,7),
                                    c(3,8),
                                    c(3,9),
                                    c(3,10),
                                    c(3,11),
                                    c(3,12),
                                    c(3,13),
           
                                    c(4,5),
                                    c(4,6),
                                    c(4,7),
                                    c(4,8),
                                    c(4,9),
                                    c(4,10),
                                    c(4,11),
                                    c(4,12),
                                    c(4,13),
                                    
                                    c(5,6),
                                    c(5,7),
                                    c(5,8),
                                    c(5,9),
                                    c(5,10),
                                    c(5,11),
                                    c(5,12),
                                    c(5,13),
          
          
                                    c(6,7),
                                    c(6,8),
                                    c(6,9),
                                    c(6,10),
                                    c(6,11),
                                    c(6,12),
                                    c(6,13),
           
                                    c(7,8),
                                    c(7,9),
                                    c(7,10),
                                    c(7,11),
                                    c(7,12),
                                    c(7,13),
           
                                    c(8,9),
                                    c(8,10),
                                    c(8,11),
                                    c(8,12),
                                    c(8,13),
          
                                    c(9,10),
                                    c(9,11),
                                    c(9,12),
                                    c(9,13),
           
                                    c(10,11),
                                    c(10,12),
                                    c(10,13),
           
                                    c(11,12),
                                    c(11,13),
                                    
                                    c(12,13)
                         ), 
           
                         test.centrality = TRUE,
                         centrality = c("closeness",
                                        "betweenness",
                                        "strength",
                                        "expectedInfluence"),
                         nodes = 1:13, # List all nodes other than age and sex
                         p.adjust.methods = "bonferroni"
                         )

networkcomparison_no_BE_v_BE_no_loss_control
```

### 5. Global strength: No BE vs BE no loss control differences 
```{r No BE vs BE no loss control Network Comparison Test results - global strength}
networkcomparison_no_BE_v_BE_no_loss_control$glstrinv.sep # global strength of each network - adding up all the networks in each network, is there a difference?
networkcomparison_no_BE_v_BE_no_loss_control$glstrinv.real # difference in global strength
networkcomparison_no_BE_v_BE_no_loss_control$glstrinv.pval # significance of difference in global strength

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/global_strength_plot_no_BE_vs_BE_no_loss_control.png")) 

plot(networkcomparison_no_BE_v_BE_no_loss_control, what = "strength") # the results of the global strength test can be plotted

dev.off()
```

### 6. Network structure: No BE vs BE no loss control differences 
Results can also be plotted. The permutation test results in a reference distribution of test statistics under the relevant null hypothesis. NCT is accompanied by a plotting function to visualizethe results. The red triangle indicates the test statistics based on the observed (real) data.
IF 0, just say p < 0.001
```{r No BE vs BE no loss control Network Comparison Test results - network structure}
networkcomparison_no_BE_v_BE_no_loss_control$nwinv.real # max difference in network structure
networkcomparison_no_BE_v_BE_no_loss_control$nwinv.pval # significance of difference in structure/organisation

png(file = paste0(filepath_plots, "/symptom/sensitivity_analysis/2.Be_no_loss_control/network_structure_plot_no_BE_vs_BE_no_loss_control.png")) 

plot(networkcomparison_no_BE_v_BE_no_loss_control, # the results of the network structure test can be plotted
     what = "network")

dev.off()
```

### 6a. If significant - SPECIFIC EDGE WEIGHT DIFFERENCES 
NB: When writing up, will need to refer back to the networks to see which edge weight was stronger and in which model. This only tells you if the difference was significant, not in which direction.
```{r No BE vs BE no loss control Network Comparison Test results - specific edge weights}
networkcomparison_no_BE_v_BE_no_loss_control$einv.real # difference in edge weights of OBSERVED networks
networkcomparison_no_BE_v_BE_no_loss_control$einv.pvals # The Holm-Bonferroni corrected p values per edge from the permutation test concerning differences in edges weight
networkcomparison_no_BE_v_BE_no_loss_control$einv.perm # The values of the difference in edge weight of the permuted networks. Only iftest.edges =TRUE 
# plot(networkcomparison_ANBP_BN, # The distribution(s) of the edge strength invariance test can be plotted
 #    what="edge")
```

### 7. Significant centrality differences
```{r No BE vs BE no loss control Network Comparison Test results - significant differences centrality}
networkcomparison_no_BE_v_BE_no_loss_control$diffcen.real # The values of the difference in centralities of the OBSERVED networks. 
networkcomparison_no_BE_v_BE_no_loss_control$diffcen.perm # The values of the difference in centralities of the PERMUTED networks. 
networkcomparison_no_BE_v_BE_no_loss_control$diffcen.pval # p-values (corrected for multiple testing or not according to ’p.adjust.methods’) per node from the permutation test concerning differences in centralities. 
```

# Compare centrality indices: MULTIPLE COMPARISONS
```{r Compare centrality indicies both}
centralityplot <- centralityPlot(list("Binge eating (with loss of control)" = BE_network_bootnet,
                                      "Overeating (no loss of control)" = BE_no_loss_control_network_bootnet,
                                      "No binge eating or overeating" = no_BE_network_bootnet),
                                      include = "ExpectedInfluence",
                                      orderBy = "ExpectedInfluence",
                                      labels = longnames)

png(file = paste0(filepath_plots, "/revised_symptom/centrality_diff_sens_loss_control",date,".png"))

centralityplot + 
   labs(x = "Centrality indices",
            y = "Nodes",
            colour = "Comparison group")

dev.off()
```
